### 2016-12-15 Objects/Objects.tex
Adding plots to objects section

\begin{figure}
\includegraphics[width=0.5\textwidth]{./Objects/Plots/PrimaryVertexRes.png}
\caption{Resolution of the z--coordinate of reconstructed primary vertices
as a function of the number of tracks associated with the vertex, 
for minimum--bias events in red and for
events with many jets in black. The resolution improves
with larger numbers of tracks \cite{cms-trk-algos}.}
\label{fig:objects_tracks_pvres}
\end{figure}

@@

@@

%The presence of a secondary vertex, and kinematic quantities associated with it, 
%are helpful in distinguishing between b-- and lighter jets. Secondary
%vertices are reconstructed by selecting high--purity tracks within
%a cone of $\Delta R = 0.3$ around the jet axis, which are
%fitted using an adaptive vertex fit as for primary vertex reconstruction (section \ref{sec:objects_tracks}).
%For the \ac{CSV} algorithm, secondary vertices need to share less than 65\% of associated tracks
%with the primary vertex, and the significance of the radial distance between the two vertices
%must exceed $3\sigma$. The flight direction of each candidate has to be within a cone
%of $\Delta R < 0.5$ around the jet direction. Secondary vertices which are more
%than 2.5 cm away from the primary vertex and whose mass is either compatible
%with that of a \PKzero or exceeds $6.5$ GeV are rejected to reduce the contamination
%from vertices produced due to interactions of particles with the detector
%material or decays of long--lived particles. The information from the selected
%secondary vertices is then combined with information about the tracks in the jet,
%to form two likelihood ratios to discriminate between b- and c- jets and 
%between b- and light jets. These likelihood ratios are combined into one
%a single discriminant.
The \ac{CSV}v2 algorithm as improved for Run 2
uses an \ac{IVF} algorithm to reconstruct secondary vertices \cite{cms-ivf}. Instead of 
using only tracks near the jet, in this algorithm all reconstructed
tracks in the event which are displaced from the primary vertex are used.
In addition, the algorithm makes use of a multilayer perceptron to combine the variables
instead of constructing and combining two likelihood ratios from the input variables \cite{cms-btag-run2}. This allows
for the addition of extra variables to discriminate between b- and other jets.

@@

Systematic uncertainties in the scale factors arise from, amongst other things,
pile--up modelling in simulation, gluon splitting into $b\bar{b}$ pairs, track mismeasurement,
and uncertainties in the fractions of different jet types.

@@

Two \ac{BDTs} trained on \Zmm  are used to compute this correction.
The first one corrects the direction of the hadronic recoil, the second
one uses a data sample with the corrected recoil direction to compute a correction
to the magnitued of the hadronic recoil. The BDT regression uses the magnitude of the hadronic
recoil, the azimuthal angle and scalar \pT sum of all \ac{PF} particles for several 
different \MET definitions \cite{cms-met-run1} as input. 
In the process of calculating the corrections to the hadronic recoil using the MVA \MET
algorithm, the significance of the MVA \MET is also estimated, providing an event--by--event
estimator of the likelihood that the \MET is due to unseen objects rather than induced
by mismeasurement of jet energy \cite{cms-met-run1}.

%Further corrections improve the performance of the ⃗E/T reconstruction in events with large numbers of pileup interactions. The contribution to the genuine ⃗E/T from such interactions is
close to zero, as the probability to produce neutrinos is small in inelastic pp scattering (mini- mum bias) interactions. The vectorial ⃗pT sum of charged particles is therefore expected to be well balanced by that of neutral particles. However, the nonlinearity and minimum energy thresholds in the calorimeters cause ⃗E/ T to point on average in the direction of the vectorial ⃗pT sum of neutral particles.

@@

Figure \ref{fig:tau_iso_efficiency} compares the \Pgt identification efficiency with the
jet$\rightarrow \Pgt_{h}$ fake rate for different working points of the
MVA isolation discriminator, as well as the cut--based isolation discriminator based
on isolation sum and $p_{\text{T}}^{\text{strip,outer}}$. The MVA--based 
discriminator has better performance than the cut-based discriminator alone.

\begin{figure}
\includegraphics[width=0.7\textwidth]{./Objects/Plots/TauIsolationPlot.png}
\caption{jet$\rightarrow \Pgt_{h}$ fake rate versus $\Pgt_{h}$ identification efficiency for \htotautau events,
comparing the MVA-based discriminator in red with the cut-based isolation discriminator in pink. Tighter working points
give lower hadronic tau identification efficiencies and lower fake rates. The MVA-based discriminator
has a lower fake rate than the cut-based discrminator for the same $\Pgt_{h}$ identification efficiency \cite{cms-tau-2015}.}
\label{fig:tau_iso_efficiency}
\end{figure}

@@

Five working points are provided, ranging from very loose to very tight.

>>>>

\begin{figure}
\begin{center}
\subfloat[Resolution in x]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/PVResX.png}}
\subfloat[Resolution in z]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/PVResZ.png}}
\end{center}
\caption{Resolution of the x-- (a) and z--coordinate  (b)
of reconstructed primary vertices
as a function of the scalar sum \pT of the tracks, 
measured for the 2015 running conditions in blue triangles
and for 2016 in red squares.
The resolution improves
with higher sum \pT (generally corresponding to larger numbers of tracks) \cite{cms-trk-dp}.}
\label{fig:objects_tracks_pvres}
\end{figure}

@@

Figure \ref{fig:ele_id_vars} shows the distributions of $\sigma_{i\eta,i\eta}$ and $1/E_{sc} - 1/p_e$ 
for real and misidentified electrons in the full dataset from the 2012 running period of the \ac{LHC}.

\begin{figure}
\begin{center}
\subfloat[$\sigma_{i\eta,i\eta}$]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/Sigmaietaieta.png}}
\subfloat[$1/E_{\text{SC}} - 1/p_{e}$]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/OneoverEminOneoverp.png}}
\end{center}
\caption{$\sigma_{i\eta,i\eta}$ (a) and $1/E_{\text{SC}} - 1/p_{e}$ (b) for real (black points)  and 
misidentified electrons (yellow triangles) in a dataset corresponding to 19.7 fb$^{-1}$
taken at $\sqrt{s} = 8$ TeV, overlaid on the variables for simulated 
real electrons in purple \cite{cms-elereco-run1}.}
\label{fig:ele_id_vars}
\end{figure}

@@

%The presence of a secondary vertex, and kinematic quantities associated with it, 
%are helpful in distinguishing between b-- and lighter jets. Secondary
%vertices are reconstructed by selecting high--purity tracks within
%a cone of $\Delta R = 0.3$ around the jet axis, which are
%fitted using an adaptive vertex fit as for primary vertex reconstruction (section \ref{sec:objects_tracks}).
%For the \ac{CSV} algorithm, secondary vertices need to share less than 65\% of associated tracks
%with the primary vertex, and the significance of the radial distance between the two vertices
%must exceed $3\sigma$. The flight direction of each candidate has to be within a cone
%of $\Delta R < 0.5$ around the jet direction. Secondary vertices which are more
%than 2.5 cm away from the primary vertex and whose mass is either compatible
%with that of a \PKzero or exceeds $6.5$ GeV are rejected to reduce the contamination
%from vertices produced due to interactions of particles with the detector
%material or decays of long--lived particles. The information from the selected
%secondary vertices is then combined with information about the tracks in the jet,
%to form two likelihood ratios to discriminate between b- and c- jets and 
%between b- and light jets. These likelihood ratios are combined into one
%a single discriminant.
The \ac{CSV}v2 algorithm as improved for Run 2
uses an \ac{IVF} algorithm to reconstruct secondary vertices \cite{cms-ivf}. Instead of 
using only tracks near the jet, in this algorithm all reconstructed
tracks in the event which are displaced from the primary vertex are used.
In addition, the algorithm makes use of a multilayer perceptron to combine the variables
instead of constructing and combining two likelihood ratios from the input variables \cite{cms-btag-run2}. This allows
for the addition of extra variables to discriminate between b- and other jets. Figure \ref{fig:objects_bjets}a shows
the distribution of the \ac{CSV}v2 discriminator in multijet events in the 2015 data sample.

@@

Systematic uncertainties in the scale factors arise from, amongst other things,
pile--up modelling in simulation, gluon splitting into $b\bar{b}$ pairs, track mismeasurement,
and uncertainties in the fractions of different jet types.
Figure \ref{fig:objects_bjets}b shows the b--tagging scale factors, and associated errors,
for the medium working point of the \ac{CSV}v2 discriminator in the
2015 data sample.

\begin{figure}
\begin{center}
\subfloat[CSVv2 distribution]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/CSVDistributionMultijet.pdf}}
\subfloat[CSVv2 scale factors]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/CSVSF.png}}
\end{center}
\caption{(a) distribution of CSVv2 discriminant for multijet events in 2.6 fb$^{-1}$ 
collected at $\sqrt{s} = 13$ TeV and (b) the b--scale factors and errors
as a function of jet \pT for the medium working point of the CSVv2 discriminant \cite{cms-btag-run2}.}
\label{fig:objects_bjets}
\end{figure}

@@

Two \ac{BDTs} trained on \Zmm  are used to compute this correction.
The first one corrects the direction of the hadronic recoil, the second
one uses a data sample with the corrected recoil direction to compute a correction
to the magnitued of the hadronic recoil. The BDT regression uses the magnitude of the hadronic
recoil, the azimuthal angle and scalar \pT sum of all \ac{PF} particles for several 
different \MET definitions \cite{cms-met-run1} as input. Figure \ref{fig:objects_mvamet} shows
the performance of the MVA \MET in data collected at $\sqrt{s}=13$ TeV compared with 
the \ac{PF} \MET, indicating the lower MVA \MET values for events without genuine
\MET in figure \ref{fig:objects_mvamet}a and the improved resolution at high pile--up
in figure \ref{fig:objects_mvamet}b.

\begin{figure}
\begin{center}
\subfloat[\MET distribution in \Zmm events]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/Met_Data.png}}
\subfloat[\MET resolution]{\includegraphics[width=0.5\texwidth]{./Objects/Plots/transverse_resolution_npv.png}}
\end{center}
\caption{(a) \MET distributions comparing MVA \MET (brown circles) to \ac{PF} \MET (black circles) for
\Zmm events, which contain no genuine \MET, in a sample corresponding to 42 pb${-1}$ of data collected at $\sqrt{s}=13$ TeV. The \MET
values for MVA \MET are lower than for \ac{PF} \MET. (b) the \MET resolution for \ac{PF} \MET in blue and MVA \MET in red/brown
circles, as a function of number of vertices. The MVA \MET resolution is more stable with increased pile--up \cite{cms-dp-mvamet}.}
\label{fig:objects_mvamet}
\end{figure}

In the process of calculating the corrections to the hadronic recoil using the MVA \MET
algorithm, the significance of the MVA \MET is also estimated, providing an event--by--event
estimator of the likelihood that the \MET is due to unseen objects rather than induced
by mismeasurement of jet energy \cite{cms-met-run1}.

%Further corrections improve the performance of the ⃗E/T reconstruction in events with large numbers of pileup interactions. The contribution to the genuine ⃗E/T from such interactions is
%close to zero, as the probability to produce neutrinos is small in inelastic pp scattering (mini- mum bias) interactions. The vectorial ⃗pT sum of charged particles is therefore expected to be well balanced by that of neutral particles. However, the nonlinearity and minimum energy thresholds in the calorimeters cause ⃗E/ T to point on average in the direction of the vectorial ⃗pT sum of neutral particles.

@@

Figure \ref{fig:tau_iso_efficiency}a compares the \Pgt identification efficiency with the
jet$\rightarrow \Pgt_{h}$ fake rate for different working points of the
MVA isolation discriminator, as well as the cut--based isolation discriminator based
on isolation sum and $p_{\text{T}}^{\text{strip,outer}}$. The MVA--based 
discriminator has better performance than the cut-based discriminator alone.

@@

Five working points are provided, ranging from very loose to very tight. The real tau efficiency
and $Pe\rightarrow\Pgt_h$ fake rate for the various working points are shown in
figures \ref{fig:tau_efficiency}b and c, respectively.

\begin{figure}
\begin{center}
\subfloat[Isolation performance]{\includegraphics[width=0.5\textwidth]{./Plots/Objects/TauEfficiencyIsol.pdf}}\\
\subfloat[Anti-e discriminator efficiency]{\includegraphics[width=0.5\textwidth]{./Plots/Objects/TauEfficiencyEle.pdf}}
\subfloat[Anti-e discriminator fake rate]{\includegraphics[width=0.5\textwidth]{./Plots/Objects/TauMisIDEle.pdf}}
\end{center}
\caption{(a) the jet$\rightarrow\Pgt_{h}$ fake rate in QCD \ac{MC} events versus $\Pgt_{h}$ identification
efficiency for \htotautau \ac{MC} events, comparing the MVA-based isolation discriminator in red with the cut-based 
isolation discriminator in pink. Tighter working points give lower hadronic tau identification
efficiencies and lower fake rates, and for the same $\Pgt_{h}$ identification efficiency the fake rate
from the MVA-based discriminator is lower than from the cut-based discriminator. (b) the real $\Pgt_{h}$ identification
efficiency for different working points of the anti-electron discriminator, as a function of $\Pgt_{h}$ \pT, and (c)
the $\Pe\rightarrow\Pgt_{h}$ fake rate for different working points of the anti-electron discriminator, as a function of
\Pe \pT.}
\label{fig:tau_efficiency}
\end{figure}
